### 2020-05-30 writeup/experiments.tex
update table layout

\begin{table}
\begin{center}
  \begin{tabular}{c c c c c}
  \toprule
    \multirow{2}{*}{{\bf Threshold}}  & \multicolumn{2}{c}{{\bf Text classification}} & \multicolumn{2}{c}{{\bf ChestX-ray14}} \\
    & Precision &  Recall & Precision &  Recall \\
    \cmidrule(lr){1-1} \cmidrule(lr){2-3} \cmidrule(lr){4-5}
    0.0 & 0.596 & 1.000 & 0.593 & 1.000 \\
    0.1 & 0.756 & 0.388 & 0.738 & 0.462 \\
    0.2 & 0.919 & 0.065 & 0.875 & 0.044 \\	
    0.3 & 1.000 & 0.004 &     - &     - \\
  \bottomrule
  \end{tabular}
\end{center}
\caption{Ablation study on when should use MTL via different source/target task accuracy.}
\label{tab:mtl_better_than_stl}
\end{table}

@@

\begin{table}
	\begin{center}
		\begin{tabular}{c c c c c}
		\toprule
		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
		MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}MR, SST, SUBJ, CR, MPQA\end{center}\end{minipage}} \\
		\cmidrule(lr){2-3} \cmidrule(lr){4-5}
		& {\bf Standard} & {\bf Alignment} & {\bf Standard} & {\bf Alignment} \\
		\midrule
		{\bf MLP}  & > 100\% & 39\% & 25\% & 25\% \\
		{\bf LSTM} & 36\% & 36\% & 28\% & 25\% \\
		% {\bf CNN}  & 76\% & - & 32\% & -\\
		\bottomrule
		\end{tabular}
	\end{center}
	\caption{Taskonomy experiment.}
	\label{tab:taskonomy}
	\end{table}

>>>>

\begin{table}
	\centering
	\subfloat[Ablation study on when should use MTL via different source/target
	task accuracy.\label{tab:mtl_better_than_stl}]{%
  \begin{tabular}{c c c c c}
	\toprule
		\multirow{2}{*}{{\bf Threshold}}  & \multicolumn{2}{c}{{\bf Text
		classification}} & \multicolumn{2}{c}{{\bf ChestX-ray14}} \\
		& Precision &  Recall & Precision &  Recall \\
		\cmidrule(lr){1-1} \cmidrule(lr){2-3} \cmidrule(lr){4-5}
		0.0 & 0.596 & 1.000 & 0.593 & 1.000 \\
		0.1 & 0.756 & 0.388 & 0.738 & 0.462 \\
		0.2 & 0.919 & 0.065 & 0.875 & 0.044 \\	
		% 0.3 & 1.000 & 0.004 &     - &     - \\
	\bottomrule
	\end{tabular}}
	\quad% --- set horizontal distance between tables here
	\subfloat[Taskonomy experiment.\label{tab:taskonomy}]{%
	\begin{tabular}{c c c}
		\toprule
		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
		MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} \\
		\cmidrule(lr){2-3}
		& {\bf Standard} & {\bf Alignment} \\
		\midrule
		{\bf MLP}  & > 100\% & 39\% \\
		{\bf LSTM} & 36\% & 36\% \\
		\bottomrule
		\end{tabular}}
\end{table}

% \begin{table}
% \begin{center}
%   \begin{tabular}{c c c c c}
%   \toprule
%     \multirow{2}{*}{{\bf Threshold}}  & \multicolumn{2}{c}{{\bf Text classification}} & \multicolumn{2}{c}{{\bf ChestX-ray14}} \\
%     & Precision &  Recall & Precision &  Recall \\
%     \cmidrule(lr){1-1} \cmidrule(lr){2-3} \cmidrule(lr){4-5}
%     0.0 & 0.596 & 1.000 & 0.593 & 1.000 \\
%     0.1 & 0.756 & 0.388 & 0.738 & 0.462 \\
%     0.2 & 0.919 & 0.065 & 0.875 & 0.044 \\	
%     0.3 & 1.000 & 0.004 &     - &     - \\
%   \bottomrule
%   \end{tabular}
% \end{center}
% \caption{Ablation study on when should use MTL via different source/target task accuracy.}
% \label{tab:mtl_better_than_stl}
% \end{table}

@@

% \begin{table}
% 	\begin{center}
% 		\begin{tabular}{c c c c c}
% 		\toprule
% 		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
% 		MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}MR, SST, SUBJ, CR, MPQA\end{center}\end{minipage}} \\
% 		\cmidrule(lr){2-3} \cmidrule(lr){4-5}
% 		& {\bf Standard} & {\bf Alignment} & {\bf Standard} & {\bf Alignment} \\
% 		\midrule
% 		{\bf MLP}  & > 100\% & 39\% & 25\% & 25\% \\
% 		{\bf LSTM} & 36\% & 36\% & 28\% & 25\% \\
% 		% {\bf CNN}  & 76\% & - & 32\% & -\\
% 		\bottomrule
% 		\end{tabular}
% 	\end{center}
% 	\caption{Taskonomy experiment.}
% 	\label{tab:taskonomy}
% 	\end{table}
